### 2024-07-02 causal-inference.qmd
20240702 - additions

Which variables are important to be included as control variables can be informed by the use of [causal diagrams](#sec-causalDiagrams), as described in @sec-causalDiagrams.

@@

@@

@@

```{r}
dagitty::impliedConditionalIndependencies(partial_mediation)

dagitty::adjustmentSets(
  partial_mediation, 
  exposure = "x",
  outcome = "y",
  effect = "total")

dagitty::adjustmentSets(
  partial_mediation, 
  exposure = "x",
  outcome = "y",
  effect = "direct")
```

>>>>

However, it can be problematic to control for variables indiscriminantly.
The use of [causal diagrams](#sec-causalDiagrams) can inform which variables are important to be included as control variables, and—just as important—which variables not to include as control variables, as described in @sec-causalDiagrams.

@@

Mediation can be divided into two types: [full](#sec-causalDiagramMediationFull) and [partial](#sec-causalDiagramMediationPartial).
In [full mediation](#sec-causalDiagramMediationFull), the mediator(s) fully account for the effect of the predictor variable on the outcome variable.
In [partial mediation](#sec-causalDiagramMediationPartial), the mediator(s) partially but do not fully account for the the effect of the [predictor variable](#sec-correlationalStudy) on the [outcome variable](#sec-correlationalStudy).

#### Full Mediation {#sec-causalDiagramMediationFull}

@@

#### Partial Mediation {#sec-causalDiagramMediationPartial}

@@

```{r}
dagitty::impliedConditionalIndependencies(partial_mediation)
```

```{r}
dagitty::adjustmentSets(
  partial_mediation, 
  exposure = "x",
  outcome = "y",
  effect = "total")
```

```{r}
dagitty::adjustmentSets(
  partial_mediation, 
  exposure = "x",
  outcome = "y",
  effect = "direct")
```

### 2024-07-02 multiple-regression.qmd
20240702 - additions

Multiple regression examines the association between multiple [predictor variables](#sec-correlationalStudy) and one [outcome variable](#sec-correlationalStudy).
It allows obtaining a more accurate estimate of the unique contribution of a given predictor, by controlling for other variables ([covariates](#sec-covariates)).

Regression with one predictor takes the form of @eq-regression:

>>>>

Multiple regression examines the association between multiple [predictor variables](#sec-correlationalStudy) and one [outcome variable](#sec-correlationalStudy).
It allows obtaining a more accurate estimate of the unique contribution of a given [predictor variable](#sec-correlationalStudy), by controlling for other variables ([covariates](#sec-covariates)).

Regression with one [predictor variable](#sec-correlationalStudy) takes the form of @eq-regression:
